Peripheral Edema measurement methods (by ArticleAggregator_v03)

### 2022-11-08 ArticleAggregator_v05_pure.qmd
ToDo updated
ToDo update

# ToDo
- gs extract surnames that include hyphen
- Add columns: Status, Priority

>>>>

# ToDo
- gs extract surnames that include hyphen
- gs with single page outcome
- save final table with search_term name (instead of egp)
- delete variables after writing to xlsx_to_merge
- delete temporary files (to_marge, PubMed.xml etc.)
